Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 policies.tex
Change "overheads" to "overhead".

In order to use partial monitoring to enable adjustable overheads, we must also
specify a policy for when and which monitoring events are dropped. In this
section, we discuss some of the options and trade-offs for dropping policies.
We split this decision into two components: \begin{enumerate} \item When do we
need to drop events in order to enable reduced overheads?
(Section~\ref{sec:policies.when}) \item Which events should be dropped?
(Section~\ref{sec:policies.which}) \end{enumerate}

@@

In this section, we discuss two possible ways to determine when events should
be dropped.  The first possibility is to probabilistically drop events. By
setting the probability of dropping events appropriately, overheads can be
reduced. This works well for enabling partial monitoring for cooperative
testing and debugging since the randomness allows different users and runs to
monitor different portions of the program. However, using a probabilistic
dropping policy can make it difficult to meet a target overhead without prior
profiling.

Alternatively, we can specify a target overhead and estimate, at run-time, the
overheads of monitoring in order to decide whether dropping is needed.  The
overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. In order to estimate overheads at run-time, we
define \emph{slack} as the number of cycles of monitoring overhead that can be
incurred while staying within the budget target. Slack is essentially the
difference between the actual overhead seen and the budget specified. Slack is
generated as the main program runs and consumed as monitoring overheads occur.
For example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles.  In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over
time.  In this slack-based policy, if the slack falls below zero (i.e., the
overhead budget is exceeded), then monitoring events are dropped.

@@

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overheads, then a probabilistic,
source-only dropping policy can be used to provide good total coverage over
multiple runs.
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping. Sub-flow dropping matches overheads better than
source-only dropping and provides better coverage than unrestricted dropping.
For a probabilistic policy, sub-flow dropping allows better overhead matching
while still allowing good total coverage over multiple runs, though at a slower
rate than source-only dropping.

>>>>

In order to use partial monitoring to enable adjustable overhead, we must also
specify a policy for when and which monitoring events are dropped. In this
section, we discuss some of the options and trade-offs for dropping policies.
We split this decision into two components: \begin{enumerate} \item When do we
need to drop events in order to enable reduced overhead?
(Section~\ref{sec:policies.when}) \item Which events should be dropped?
(Section~\ref{sec:policies.which}) \end{enumerate}

@@

In this section, we discuss two possible ways to determine when events should
be dropped.  The first possibility is to probabilistically drop events. By
setting the probability of dropping events appropriately, overhead can be
reduced. This works well for enabling partial monitoring for cooperative
testing and debugging since the randomness allows different users and runs to
monitor different portions of the program. However, using a probabilistic
dropping policy can make it difficult to meet a target overhead without prior
profiling.

Alternatively, we can specify a target overhead and estimate, at run-time, the
overhead of monitoring in order to decide whether dropping is needed.  The
overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. In order to estimate the overhead at run-time, we
define \emph{slack} as the number of cycles of monitoring overhead that can be
incurred while staying within the budget target. Slack is essentially the
difference between the actual overhead seen and the budget specified. Slack is
generated as the main program runs and consumed as monitoring overheads occur.
For example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles.  In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over
time.  In this slack-based policy, if the slack falls below zero (i.e., the
overhead budget is exceeded), then monitoring events are dropped.

@@

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overhead, then a probabilistic,
source-only dropping policy can be used to provide good total coverage over
multiple runs.
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping. Sub-flow dropping matches overhead better than
source-only dropping and provides better coverage than unrestricted dropping.
For a probabilistic policy, sub-flow dropping allows better overhead matching
while still allowing good total coverage over multiple runs, though at a slower
rate than source-only dropping.

### 2015-01-05 related.tex
Change "overheads" to "overhead".

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overheads. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overheads but does not try
  to bound overheads, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

For example, there exists previous work for using statistical sampling to
reduce the performance overheads of various debugging techniques. These include
sampling for bug isolation \cite{liblit-pldi05}, memory leak detection
\cite{chilimbi-asplos04}, race detection \cite{literace-pldi09, pacer-pldi10},
and information flow tracking \cite{testudo-micro08, greathouse-cgo11}. These
techniques modify the monitoring to support statistical sampling and so are not
generalizable. For those that prevent false positives, this is also done with
monitor-specific modifications. Finally, with the exception of the work by
Greathouse et al. \cite{greathouse-cgo11}, they do not allow an overhead target
to be specified.

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overheads
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overheads. QVM does prevent false positives
but does so by enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.

>>>>

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overhead. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overhead but does not try
  to bound overhead, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

For example, there exists previous work for using statistical sampling to
reduce the performance overhead of various debugging techniques. These include
sampling for bug isolation \cite{liblit-pldi05}, memory leak detection
\cite{chilimbi-asplos04}, race detection \cite{literace-pldi09, pacer-pldi10},
and information flow tracking \cite{testudo-micro08, greathouse-cgo11}. These
techniques modify the monitoring to support statistical sampling and so are not
generalizable. For those that prevent false positives, this is also done with
monitor-specific modifications. Finally, with the exception of the work by
Greathouse et al. \cite{greathouse-cgo11}, they do not allow an overhead target
to be specified.

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overhead
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overhead. QVM does prevent false positives
but does so by enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.
